### 2023-10-05 latex/paper/main.tex
comments
updated paper

\subsubsection{Cluster architecture}

@@

\begin{lstlisting}[language=Python, caption={inv\_calc}]
    @ray.remote
    def inv_calc(row, cof_cols, cof_data, det):
        for col in range(cof_cols):
            return (row, col, (cof_data[row][col] / det))
    \end{lstlisting}
\pagebreak
\begin{lstlisting}[language=Python, caption={inv\_cof\_matrix}]
@ray.remote
def inv_cof_matrix(A, row, cols):

    cof_row = []

    for column in range(cols):
        minor = A.minor(row, column)
        cof_row.append(((-1)**(row + column)) * minor.det())

>>>>

\subsubsection{Cluster architecture}
/scrivere informazioni riguardo il cluster, come le specifiche tecniche e la quantita di macchine/

@@

\begin{lstlisting}[language=Python, caption={inv\_calc}]
    @ray.remote
    def inv_calc(row, cof_cols, cof_data, det):
        for col in range(cof_cols):
            return (row, col, (cof_data[row][col] / det))
    \end{lstlisting}
\pagebreak
\begin{lstlisting}[language=Python, caption={inv\_cof\_matrix}]
@ray.remote
def inv_cof_matrix(A, row, cols):
    from matrix import Matrix

    cof_row = []
    minor_futures = [Matrix.dist_minor.remote(A, row, col) for col in range(cols)]
    minors = ray.get(minor_futures)

    for col,minor in zip(range(cols), minors):
        cof_row.append(((-1)**(row + col)) * minor.det())
